Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-12-01 files/Overview.tex
overview

Section 4.5 is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions. (See Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. \textcolor{red}{The results show that the shape of the beam impacts the comparison. The comparison improves as the beam gets more slender, but overall the comparisons are very good.}\sout{As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.}

The next section is a discussion on the article \cite{SP06}. In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a physical beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis. The authors report on an experiment with forced vibration a free-free beam where the natural frequencies are measured. These emperical results are then compared to the theoretical results. This result, together with the results in chapter 6, give a good picture to the validity of the Timoshenko beam theory. Finally the chapter is concluded by looking at a model of a cantilever beam with a tip-body with elastic interfaces. These results combine modal analysis and investigates at the behavior of the model. A similar model using realistic two- or three-dimensional model will be very challenging.

@@

\subsubsection{Chapter 6}
In this chapter, the main comparisons of the models are conducted. All of the sections follow the same idea and struture as the article \cite{LVV09}.

@@

But in real-world applications, a beam is a three-dimensional model. Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory. This is mentioned by the authors of \cite{LVV09}. Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities. Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference. Again the results so that the comparison relies on the shape of the beams. The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.

\section{500-word summary}
This dissertation is a literature study that investigates the validity of different linear models in application. Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models. This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory. The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate. In the first chapter, the models are provided.

Next, a discussion of the existence and uniqueness of solutions for a general vibration problem. The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution. The authors then prove this is also a solution of the general vibration problem. An application of this theory is demonstrated using a cantilever Timoshenko beam.

Thereafter a discussion of two theoretical results for the Finite Element Method. The first result is from an article where the convergence of the Galerkin Approximation is proved. A Galerkin Approximation of the general vibration problem is derived. Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution. The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem. The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem. This section rewrites the textbook's results with updated notation, aiming for greater clarity and understanding.

The forth chapter discusses results for the Timoshenko beam theory. First an article is examined that provides a method to calculate the exact eigenvalues and eigenvectors. The method is then applied to a cantilever and a free-free beam model. Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory. Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces. This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.

In the fifth chapter, the Finite Element Method is applied to the two and three-dimensional models of this dissertation. The goal of this chapter is to obtain a numerical formula that can be used to calculate the eigenvalues and eigenvectors of the models in preparation for the final chapter where the models are compared.

The last chapter compares the eigenvalues and eigenvectors of the models. The approach is based on an article where a cantilever Timoshenko beam model is compared to a cantilever two-dimensional model. The article is discussed and results replicated. The article is then extended to a comparison of a two-dimensional model to a three-dimensional model. Finally, a cantilever Reissner-Mindlin plate model is compared to a cantilever three-dimensional plate model.

\textcolor{red}{493 Words}

@@

In this chapter, two convergence results relating to the Finite Element Method are discussed. The first result is the convergence of the Galerkin approximation for vibration problems. This is presented in the article \cite{BV13.} For this result, the general variational form of Chapter 2 is used. The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices. The article \cite{BV13} derive an error estimate for the solution of the general vartiational problem and the solution to it's Galerkin approximation. To obtain this error estimate, the authors make two assumptions, and split the problem into a semi-discrete and a fully discrete problem. Following the assumptions, the authors prove error estimates for the semi-dicrete and the fully-discrete problem.\\

>>>>

Section 4.5 is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions. (See Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. \textcolor{red}{The results improve as the beam gets more slender. This shows that the shape of the beam is important. The cases covered are realistic to applications.}\sout{As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.}

The next section is a discussion on the article \cite{SP06}. In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a physical beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis. The authors report on an experiment with forced vibration a free-free beam where the natural frequencies are measured. These empirical results are then compared to the theoretical results. This result, together with the results in chapter 6, give a good picture to the validity of the Timoshenko beam theory. \sout{Finally the chapter is concluded by looking at a model of a cantilever beam with a tip-body with elastic interfaces. These results combine modal analysis and investigates at the behavior of the model. A similar model using realistic two- or three-dimensional model will be very challenging.}

@@

\subsubsection{Chapter 6}
\textcolor{red}{This chapter is an extension of the work of Section 4.5. In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.}

In real-world applications, a beam is a three-dimensional model. Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory. This is mentioned by the authors of \cite{LVV09}. Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities. Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference. Again the results so that the comparison relies on the shape of the beams. The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.

\sout{In this chapter, the main comparisons of the models are conducted. All of the sections follow the same idea and struture as the article \cite{LVV09}.}

@@

\section{500-word summary}
This dissertation is a literature study that investigates the validity of different linear models in application. Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models. This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory. The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate. The models are provided in the first chapter

Next, a discussion of the existence and uniqueness of solutions for a general vibration problem. The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution. The authors then prove this is also a solution of the general vibration problem. An application of this theory is demonstrated using a cantilever Timoshenko beam. \textcolor{red}{Modal analysis is crucial to this dissertation. We show that the solution of the general vibration problem is a linear combination of the eigenvalues and eigenfunctions. This is the foundation of the comparisons of the models in this dissertation.}

Thereafter a discussion of two theoretical results for the Finite Element Method. The first result is from an article where the convergence of the Galerkin Approximation is proved. \sout{A Galerkin Approximation of the general vibration problem is derived.} Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution. The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem. The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem. This is based of work done in a textbook, but the notation is updated and some proofs are expanded.

The forth chapter discusses results for the Timoshenko beam theory. First an article is examined that provides a method to calculate the exact eigenvalues and eigenvectors. The method is then applied to a cantilever and a free-free beam model. \textcolor{red}{Thereafter, the validity of the Timoshenko beam theory is investigated, by comparing a Timoshenko beam model to a two-dimensional beam model. The comparison is made by comparing the eigenvalues and eigenvectors.} Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory. \sout{Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces. This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.}

In the fifth chapter, the Finite Element Method is applied to the two and three-dimensional models of this dissertation. The goal of this chapter is to obtain a numerical formula \textcolor{red}{to solve the eigenvalue problems,} \sout{that can be used to calculate the eigenvalues and eigenvectors of the models in} preparation for the final chapter where the models are compared.

The last chapter extends the numerical results of the dissertation to a comparison of a two-dimensional model to a three-dimensional beam model and a comparison of a Reissner-Mindlin plate model to a three-dimensional plate model.

\textcolor{red}{WORD COUNT: 470}

@@

In this chapter, two convergence results relating to the Finite Element Method are discussed. The first result is the convergence of the Galerkin approximation for vibration problems. This is presented in the article \cite{BV13.} For this result, the general variational form of Chapter 2 is used. The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices. The article \cite{BV13} derive an error estimate for the solution of the general varitat problem and the solution to it's Galerkin approximation. To obtain this error estimate, the authors make two assumptions, and split the problem into a semi-discrete and a fully discrete problem. Following the assumptions, the authors prove error estimates for the semi-dicrete and the fully-discrete problem.\\
